---
title: "Campus Recruitment Project"
author: "Katie Monroe"
date: "11/17/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plyr)
library(gtsummary)
library(qwraps2)
library(fBasics)
library(GGally)
library(MASS)
library(randomForest)
library(e1071)
library(knitr)
library(caret)
library(ggpubr)
library(htmlTable)
library(kableExtra)
library(magick)
```

### Project Overview 

The three goals are as follows:
1. Exploratory data analysis
2. Binary classification of placement
3. Feature selection analysis 

### Exploratory data analysis 

The variable: 
1. Gender (gender)
2. ssc_p (secondary education percentage)
3. ssc_b (board of education)
4. hsc_p (higher secondary education percentage)
5. hsc_b (board of education)
6. hsc_s (specialization in higher secondary education)
7. degree_p (degree percentage)
8. degree_t (under graduation degree field)
9. workex (work experience)
10. etest_p (employable test percentage)
11. Feature specialization (post graduate specialization)
12. Feature: mba_p (MBA percentage)

We use the following data:
1. Gender
2. Secondary Education percentage
3. Higher Secondary Education Percentage
4. Specialization in Higher Secondary Education
5. Under Graduate Degree Percentage
6. Under Graduation Degree Field
7. Work Experience
8. Employable Test Percentage
9. Specialization
10. MBA Percentage

### The first step is to prepare the data

```{r}
#read in the data
data <- read.csv("Placement_Data_Full_Class.csv",
         sep = ",", header = TRUE)

#remove sl_no, ssc_b, hsc_p, sl_no, salary, status 
visdata <- subset(data, select = -c(sl_no, ssc_b, hsc_b, sl_no, salary))

#create visual analysis 
visdata %>% tbl_summary() %>% add_stat_label()

```

### Then create visualizations for categorical data first (need to add tables)
```{r}

#for gender 

#rename gender 
visdata$gender[visdata$gender == "M"] <- "Male"
visdata$gender[visdata$gender == "F"] <- "Female"

#create table and data frame
table(visdata$gender, visdata$status)
gender <- data.frame(Gender = c("Female", "Male", "Female", "Male"), Count = c(28, 39, 48, 100), Placement = c("Not Placed", "Not Placed", "Placed", "Placed"))

#create plot
g1 <- ggplot(gender, aes(x= Gender, y = Count, fill = Placement))+
  geom_bar(stat = "identity", color = "black", position="dodge")+
  geom_text(aes(label=Count), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  theme_classic()+
   scale_fill_manual(values = c("honeydew2", "forestgreen"))+
  labs(title = "Barplot by Gender")

#for hsc_s (specialization in higher secondary education)
#create table and data frame
table(visdata$hsc_s, visdata$status)
special <- data.frame(specialization = c("Arts", "Commerce", "Science", "Arts", "Commerce", "Science"), Count =c(5,34,28,6,79,63), Placement = c("Not Placed","Not Placed","Not Placed", "Placed","Placed","Placed"))

#create plot
g2 <- ggplot(special, aes(x= specialization, y = Count, fill = Placement))+
  geom_bar(stat = "identity", color = "black", position="dodge")+
  geom_text(aes(label=Count), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  theme_classic()+
   scale_fill_manual(values = c("honeydew2", "forestgreen"))+
  labs(title = "Barplot by Specialization in Higher Secondary Education")


#for degree_t (under graduation degree field)
#create table and data frame
table(visdata$degree_t, visdata$status)
GraduateDegree <- data.frame(Degree = c("Comm&Mgmt", "Others", "Sci&Tech","Comm&Mgmt", "Others", "Sci&Tech"), Count =c(43,6,18,102,5,41), Placement = c("Not Placed","Not Placed","Not Placed", "Placed","Placed","Placed"))

#create plot
g3 <- ggplot(GraduateDegree, aes(x= Degree, y = Count, fill = Placement))+
  geom_bar(stat = "identity", color = "black", position="dodge")+
  geom_text(aes(label=Count), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  theme_classic()+
   scale_fill_manual(values = c("honeydew2", "forestgreen"))+
  labs(title = "Barplot by Under Graduation Degree Field")


#for workex (Work Experience)
#create table and data frame
table(visdata$workex, visdata$status)
WorkExperience <- data.frame(Experience = c("No", "Yes", "No","Yes"), Count =c(57,10,84,64), Placement = c("Not Placed","Not Placed","Placed","Placed"))

#create plot
g4 <- ggplot(WorkExperience, aes(x= Experience, y = Count, fill = Placement))+
  geom_bar(stat = "identity", color = "black", position="dodge")+
  geom_text(aes(label=Count), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  theme_classic()+
   scale_fill_manual(values = c("honeydew2", "forestgreen"))+
  labs(title = "Barplot by Work Experience")

#For Feature Specialization (post grad specialization)
#create table and data frame
table(visdata$specialisation, visdata$status)
PostGradSpecialization <- data.frame(PostSpecial = c("Mkt&Fin", "Mkt&Hr", "Mkt&Fin","Mkt&Hr"), Count =c(25,42,95,53), Placement = c("Not Placed","Not Placed","Placed","Placed"))

#create plot
g5 <- ggplot(PostGradSpecialization, aes(x= PostSpecial, y = Count, fill = Placement))+
  geom_bar(stat = "identity", color = "black", position="dodge")+
  geom_text(aes(label=Count), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5)+
  theme_classic()+
   scale_fill_manual(values = c("honeydew2", "forestgreen"))+
  labs(title = "Barplot by Post Grad Specialization")


```


### Now do numerical variables 

```{r}

#for ssc_p (secondary education percentage)

g6 <- ggplot(visdata, aes(x = ssc_p, fill = status)) + 
  geom_density(alpha = 0.6) + 
  theme_classic() +
  labs(title = "Histogram of Secondary Education Percentage")+
  scale_fill_manual(values = c("honeydew2", "forestgreen"))

#for hsc_p (higher secondary education percentage)

g7 <- ggplot(visdata, aes(x = hsc_p, fill = status)) + 
  geom_density(alpha = 0.6) + 
  theme_classic() +
  labs(title = "Histogram of Higher Secondary Education Percentage")+
  scale_fill_manual(values = c("honeydew2", "forestgreen"))

#for degree_p (degree percentage)

g8 <- ggplot(visdata, aes(x = degree_p, fill = status)) + 
  geom_density(alpha = 0.6) + 
  theme_classic() +
  labs(title = "Histogram of Degree Percentage")+
  scale_fill_manual(values = c("honeydew2", "forestgreen"))

#for etest_p (employability test percentage)

g9 <- ggplot(visdata, aes(x = etest_p, fill = status)) + 
  geom_density(alpha = 0.6) + 
  theme_classic() +
  labs(title = "Histogram of Employability Test Percentage")+
  scale_fill_manual(values = c("honeydew2", "forestgreen"))

#for mba_p (MBA percentage)

g10 <- ggplot(visdata, aes(x = mba_p, fill = status)) + 
  geom_density(alpha = 0.6) + 
  theme_classic() +
  labs(title = "Histogram of MBA Percentage")+
  scale_fill_manual(values = c("honeydew2", "forestgreen"))

#correlations for numerical data

nums <- unlist(lapply(visdata, is.numeric))
numdata <- visdata[ , nums]

g11 <- ggpairs(numdata)

### summary table for numerical data
basicStats(numdata)


```


### Classification and Feature Selection

```{r}

#split into training and testing
set.seed(300)
visdata$status <- as.factor(visdata$status)
ind <- sample(2, nrow(visdata), replace = TRUE, prob = c(0.75, 0.25))
train <- visdata[ind==1,]
test <- visdata[ind==2,]

#create models
#glm
glmm <- train(status ~ .,data=train,method="glm")

#create table
glmp <- predict(glmm, test)
kable(table(glmp, test$status))

#this saves the table
# htmlTable(table(glmp, test$status)) %>%
#  save_kable(file = "glmtable.png")

#show variable importance
V1 <- varImp(glmm)

g12 <- plot(V1, col = "darkgreen", main = "General Linear Model Feature Importance")

#random forest

#create model
rfm <- train(status ~ .,data=train,method="rf")

#create table
rfp <- predict(rfm, test)
table(rfp, test$status)

#create table
table(glmp, test$status)

#this saves the table
htmlTable(table(rfp, test$status)) %>%
 save_kable(file = "rftable.png")


#show variable importance

V2 <- varImp(rfm)
plot(V2, col = "darkgreen", main = "Random Forest Model Feature Importance")
```








